Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
omit all the import statements; down to 13 pages
After all, this is not tutorial material.

As an example to illustrate the initialize-\texttt{fit} sequence,
let us consider a supervised learning task using logistic regression.
Given the API defined above, solving this problem is as simple as:
\begin{pythoncode}
from sklearn.linear_model import LogisticRegression

clf = LogisticRegression(penalty="l1")
clf.fit(X_train, y_train)
\end{pythoncode}
In this snippet, a \texttt{LogisticRegression} estimator is first initialized by
setting the \texttt{penalty} hyper-parameter to \texttt{"l1"}, hence enabling
$\ell_1$ regularization. Other hyper-parameters (such as \texttt{C}, which
defines the strength of the regularization) are not explicitly defined and are
thus set to the default values. Upon calling \texttt{fit}, the model is then
learned from the training arrays \texttt{X\_train} and \texttt{y\_train}.
(In this example, \texttt{fit} is called solely for its side effects.)
Since all estimators share the same interface, using a different learning algorithm is
as simple as replacing the constructor (the class name).
For example, to build a random forest on
the same training data, one would simply have to replace
\texttt{LogisticRegression(penalty="l1")} in the snippet above by \\
\texttt{RandomForestClassifier()}.

@@

\begin{figure}[h]
\begin{pythoncode}
from sklearn.cluster import KMeans

km = KMeans(n_clusters=10)
km.fit(X_train)
clust_pred = km.predict(X_test)
\end{pythoncode}
\caption{Finding closest centroids for unseen data after $k$-means clustering.}
\label{kmeans-predict}
\end{figure}

@@

Since it is common to modify or filter data before feeding it to a learning
algorithm, some estimators in the library implement a \textit{transformer}
interface which defines a \texttt{transform} method. It takes as input some new
data \texttt{X\_test} and yields as output a transformed version of
\texttt{X\_test}. Preprocessing, feature selection and dimensionality reduction
algorithms are all provided as transformers within the library.  In our example,
if one wanted to preprocess the inputs \texttt{X\_train} before fitting the
logistic regression estimator, e.g., by standardizing the feature values, one
could thus simply write:
\begin{pythoncode}
from sklearn.preprocessing import StandardScaler

scaler = StandardScaler()
scaler.fit(X_train)
X_train = scaler.transform(X_train)
\end{pythoncode}
Of course, in practice, it is important to apply the same preprocessing to the
test data \texttt{X\_test}.
Since a \texttt{StandardScaler} stores the mean and standard deviation
that it computed for the training set,
applying it to an unseen test set \texttt{X\_test}
maps that into the appropriate region of feature space:
\begin{pythoncode}
X_test = scaler.transform(X_test)
\end{pythoncode}
Transformers also include a variety of learning algorithms, such as
dimension reduction (PCA, manifold learning techniques), kernel
approximation techniques, and any other approach that can be used to
derive a modified representation of the data.

@@

As an example, a logistic regression classifier
uses by default a one-vs.-rest scheme
for performing multiclass classification.
If multiclass classification based on error-correcting codes
is desired instead,
then this can achieved  using an \texttt{OutputCodeClassifier} meta-estimator
wrapping a \texttt{LogisticRegression} estimator:
\begin{pythoncode}
from sklearn.linear_model import LogisticRegression
from sklearn.multiclass import OutputCodeClassifier

ecoc_lr = OutputCodeClassifier(LogisticRegression(penalty="l1"))
\end{pythoncode}
The \texttt{OutputCodeClassifier} object
\textit{clones} the LR estimator multiple times for learning,
resulting in a set of estimator objects with the same settings
that each perform a binary classification
(see \citealt{dietterich1995solving} for the algorithm).
The snippet thus exemplifies the importance
of separating object instantiation and actual learning.

@@

\begin{figure}[h]
\begin{pythoncode}
from sklearn.pipeline import FeatureUnion, Pipeline
from sklearn.decomposition import PCA, KernelPCA
from sklearn.feature_selection import SelectKBest
from sklearn.linear_model import LogisticRegression

fu = FeatureUnion([("pca", PCA()),
                   ("kpca", KernelPCA(kernel="rbf"))])

@@

As an example, the snippet below illustrates how to find the
hyper-parameter settings of an SVM classifier (SVC)
that maximize its $F_1$ score,
through 10-fold cross-validation on the training set.
\begin{pythoncode}
from sklearn.grid_search import GridSearchCV
from sklearn.svm import SVC

param_grid = [
  {"kernel": ["linear"], "C": [1, 10, 100, 1000]},
  {"kernel": ["rbf"], "C": [1, 10, 100, 1000],
                      "gamma": [0.001, 0.0001]}
]

>>>>

As an example to illustrate the initialize-\texttt{fit} sequence,
let us consider a supervised learning task using logistic regression.
Given the API defined above, solving this problem is as simple as:\footnote{
  \texttt{import} statement are omitted for brevity
  throughout this paper.}
\begin{pythoncode}
clf = LogisticRegression(penalty="l1")
clf.fit(X_train, y_train)
\end{pythoncode}
In this snippet, a \texttt{LogisticRegression} estimator is first initialized by
setting the \texttt{penalty} hyper-parameter to \texttt{"l1"}, hence enabling
$\ell_1$ regularization. Other hyper-parameters (such as \texttt{C}, which
defines the strength of the regularization) are not explicitly defined and are
thus set to the default values. Upon calling \texttt{fit}, the model is then
learned from the training arrays \texttt{X\_train} and \texttt{y\_train}.
(In this example, \texttt{fit} is called solely for its side effects.)
Since all estimators share the same interface, using a different learning algorithm is
as simple as replacing the constructor (the class name).
For example, to build a random forest on
the same training data, one would simply have to replace
\texttt{LogisticRegression(penalty="l1")} in the snippet above by \\
\texttt{RandomForestClassifier()}.

@@

\begin{figure}[h]
\begin{pythoncode}
km = KMeans(n_clusters=10)
km.fit(X_train)
clust_pred = km.predict(X_test)
\end{pythoncode}
\caption{Finding closest centroids for unseen data after $k$-means clustering.}
\label{kmeans-predict}
\end{figure}

@@

Since it is common to modify or filter data before feeding it to a learning
algorithm, some estimators in the library implement a \textit{transformer}
interface which defines a \texttt{transform} method. It takes as input some new
data \texttt{X\_test} and yields as output a transformed version of
\texttt{X\_test}. Preprocessing, feature selection and dimensionality reduction
algorithms are all provided as transformers within the library.  In our example,
if one wanted to preprocess the inputs \texttt{X\_train} before fitting the
logistic regression estimator, e.g., by standardizing the feature values, one
could thus simply write:
\begin{pythoncode}
scaler = StandardScaler()
scaler.fit(X_train)
X_train = scaler.transform(X_train)
\end{pythoncode}
Of course, in practice, it is important to apply the same preprocessing to the
test data \texttt{X\_test}.
Since a \texttt{StandardScaler} stores the mean and standard deviation
that it computed for the training set,
applying it to an unseen test set \texttt{X\_test}
maps that into the appropriate region of feature space:
\begin{pythoncode}
X_test = scaler.transform(X_test)
\end{pythoncode}
Transformers also include a variety of learning algorithms, such as
dimension reduction (PCA, manifold learning techniques), kernel
approximation techniques, and any other approach that can be used to
derive a modified representation of the data.

@@

As an example, a logistic regression classifier
uses by default a one-vs.-rest scheme
for performing multiclass classification.
If multiclass classification based on error-correcting codes
is desired instead,
then this can achieved  using an \texttt{OutputCodeClassifier} meta-estimator
wrapping a \texttt{LogisticRegression} estimator:
\begin{pythoncode}
ecoc_lr = OutputCodeClassifier(LogisticRegression(penalty="l1"))
\end{pythoncode}
The \texttt{OutputCodeClassifier} object
\textit{clones} the LR estimator multiple times for learning,
resulting in a set of estimator objects with the same settings
that each perform a binary classification
(see \citealt{dietterich1995solving} for the algorithm).
The snippet thus exemplifies the importance
of separating object instantiation and actual learning.

@@

\begin{figure}[h]
\begin{pythoncode}
fu = FeatureUnion([("pca", PCA()),
                   ("kpca", KernelPCA(kernel="rbf"))])

@@

As an example, the snippet below illustrates how to find the
hyper-parameter settings of an SVM classifier (SVC)
that maximize its $F_1$ score,
through 10-fold cross-validation on the training set.
\begin{pythoncode}
param_grid = [
  {"kernel": ["linear"], "C": [1, 10, 100, 1000]},
  {"kernel": ["rbf"], "C": [1, 10, 100, 1000],
                      "gamma": [0.001, 0.0001]}
]
